Sample variance in weak lensing: how many simulations are required?

### 2016-01-08 Paper/paper.tex
added references

%ZH: I changed to more catchy title:
%\title{Simulating sample variance in weak lensing: effects on parameter inferences}
\title{Sample variance in weak lensing: how many simulations are required?}

@@

Constraining cosmology using weak gravitational lensing consists of
comparing a measured feature vector of dimension $N_b$ with its
simulated counterpart. An accurate estimate of the $N_b\times N_b$
feature covariance matrix $\bb{C}$ is essential to obtain accurate
parameter confidence intervals. When $\bb{C}$ is measured from a set
of simulations, an important question is how large this set should
be. To answer this question, we construct different ensembles of $N_r$
realizations of the shear field, using a common randomization
procedure that recycles the outputs from a smaller number $N_s\leq
N_r$ of independent ray-tracing $N$--body simulations.  We study
parameter confidence intervals as a function of ($N_s,N_r$) in the
range $1\leq N_s\leq 200$ and $1\leq N_r\leq 10^5$.  Previous work
\citep{DodelsonSchneider13} has shown that Gaussian noise in the
feature covariance lead, at quadratic order, to an $O(1/N_r)$
degradation of the parameter confidence intervals. Using a variety of
lensing features measured in our simulations, including shear-shear
power spectra and peak counts, we show that cubic and quartic
covariance fluctuations lead to additional $O(1/N_r^2)$ error
degradation that is not negligible when $N_r$ is only a factor of few
larger than $N_b$. We study the large $N_r$ limit, and find that a
single $N$--body simulation ($N_s=1$) can be repeatedly recycled to
produce as many as $N_r=10^5$ mutually independent shear maps. As a
result, a small number of simulations ($N_b=1$ or $2$) is sufficient
to forecast parameter confidence intervals at percent
accuracy. However, we find that in practice, a larger number of
simulations might be needed to measure accurate feature means and to
avoid parameter biases.
%ZH: I am not sure about the last sentence. I believe it is based on
%    an overly stringent reading of Fig.2, and that in fact we could
%    claim here, instead, that N_s=2 simulations are also sufficient
%    to get the correct mean.
%    See my comments at the end of the Conclusion section. 
\end{abstract}

@@

\section{Introduction}
%
Weak gravitational lensing (WL) is a promising cosmological probe for
constraining the dark energy equation of state $w$, and has been
considered by a range of past (CFHTLens \citep{cfht1,cfht2}),
%ZH: also cite COSMOS survey here...
ongoing (DES \citep{DES}) and future (LSST \citep{LSST})
%ZH: also cite Euclid and WFIRST.
experiments. In an era where cosmology is data driven, accurate
numerical simulations of shear fields are becoming important for
several reasons, including the study of baryonic effects
\citep{BaryonXiuyuan}, 
%ZH: also cite Joop Schaye's hydro-simulation papers on lensing (Semboloni et al), and earlier papers by Martin White et al...  Lloyd Knox et al... and Zentner et al... (I think all of these are in Xiuyuan's paper).
the computation of non--Gaussian statistics
\citep{PeaksJan,MinkJan,MinkPetri} 
%ZH: Add here some citations of other groups - Marian+Bernstein.... Bhuvnesh Jain et al... Refregier et al... Dietrichh+Hartmann... Shirasaki+Yoshida.. (again just copy from our previous papers).
and the  assessment of various systematics.
%ZH: cite papers by Jan+Morgan+Bard... and also Chihway Chan...Shirasaki+Yoshida.. and older ones by Dragan Huterer on photo-z errors..

A fundamental issue with predictions from simulations is that the
finite number of simulations naturally introduces fluctuations in the
forecasts, due to inevitable sample variance~\footnote{Sample variance is a broad term that has been used in the literature to describe a range of phenomena.  Throughout this paper, we use it to refer to the fluctuations in an ensemble of simulations, which represent random realizations of the same initial conditions.}.
%ZH: I think 'cosmic variance' usually refers to observations of the actual sky (which is finite).  
In general, quantities such as the mean or the variance of any feature
(e.g. the shear power spectrum at a multipole $\ell$), measured from a
finite set of simulations, will fluctuate, and can also suffer a bias.
While biases in the estimates of both the mean and the variance have
been studied extensively, the impact of fluctuations in the variance
has received comparatively less attention.  These fluctuations have,
however, been shown to have non-negligible effects on estimates of
features covariance matrices and hence on parameter constraints. In
particular, in the limit of Gaussian fluctuations, the parameter
confidence limits are degraged by a factor
$1+O(1/N_r)$~\citep{DodelsonSchneider13}.
%also cite Taylor Joachimi and Kitching -Morgan

@@

\subsection{Ray-tracing simulations of the convergence field}
\label{shearsim}
%
In this section, we describe how we constructed our shear field
ensembles. Background galaxies at redshift $z_s$ are lensed by large
scale structures between $z=0$ and $z_s$. The shape distortions due to
the cosmic shear $\pmb{\gamma}$ can be computed in terms of the dark
matter gravitational potential $\Phi(\bb{x},z)$. Because the evolution
of $\Phi$ with redshift is non--linear, it needs to be computed with
numerical simulations. We make use of the public code \texttt{Gadget2}
\citep{Gadget2}, with which we run a sequence of $200$ independent
dark--matter--only $N$--body simulations that track the evolution of
the density fluctuations. We assume a standard $\Lambda$CDM background
universe with the parameters
$(\Omega_m,\Omega_\Lambda,h,w,\sigma_8,n_s)=(0.26,0.74,0.72,-1,0.8,0.96)$.
We fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$,
and use $512^3$ particles, corresponding to a mass resolution of
$\approx 10^{10}M_\odot$.
%ZH: ``mass resolution'' here means DM particle mass ?

We assume a uniform galaxy distribution at a constant redshift $z_s=2$
(at which the simulation box has an angular size of $\theta_{\rm
  box}=3.5\mathrm{deg}$) and we discretize the mass distribution
between $z_s$ and the observer at $z=0$ with a sequence of 46 two
dimensional lenses of thickness $80\mathrm{Mpc}/h$. The surface
density on each lens plane is computed by projecting the
three--dimensional density measured from \texttt{Gadget2}
snapshots. We then apply the multi--lens--plane algorithm (see
\citep{RayTracingHartlap,RayTracingJain} for example) to trace the
deflections of $n_{ray}^2=2048^2$ light rays arranged on a square grid
of total size $\theta_{\rm box}$, from $z=0$ to $z_s$. Our
implementation of this algorithm is part of the \texttt{LensTools}
computing package we have been developing \citep{LensTools}, and have
released under the \texttt{MIT} license. Many different realizations
$r$ of the same shear field $\pmb{\gamma}_r(\pmb{\theta})$ can be
generated by picking different lens planes that lie between the
observer and $z_s$. The randomization procedure we adopt is the
following:
%ZH: we should cite some paper here. We didn't invent most of this
%procedure ourselves (except for maybe the 3-times thicker simulation
%output, and the random mixing of the planes from different N-body sims ?).

\begin{itemize}
\item For each lens-plane redshift $z_l$, select the snapshot at $z_l$ from the $i$--th $N$--body simulation, where $i$ is a random integer $i\in [1,N_s]$.
\item Choose randomly between the three orthogonal directions ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$: the lens plane will be perpendicular to this direction.
\item Choose the position of the plane along the snapshot: because the lens thickness is 1/3 the size of the box, we can cut three different slices of the simulation box for each orientation ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$. This gives a total of 9 choices for generating a lens plane out of a single $N$--body snapshot.
\item Perform a periodic random shift of the lens plane along its two directions.
%ZH: should we specify the range of the random shifts (0 to 1/2 the lens plane dimension?)
\item Repeat the above procedure for each lens-plane redshift $z_l$.
\end{itemize}  
%
This randomization procedure allows us to produce an (almost)
arbitrary number $N_r$ of shear realizations
$\pmb{\gamma}_r(\pmb{\theta})$. However, these realizations are not
guaranteed to be independent, if $N_s$ is not large enough. Using the
set of 200 independent $N$--body simulations, we construct different
ensembles with different choices of $N_s\in[1,200]$. Each of these
ensembles consists of the same number $N_r=1000$ of shear
realizations. We also build an additional ensemble with $N_s=1$ and
$N_r=10^5$ realizations. For each realization of each ensemble, we
reconstruct the convergence $\kappa_r(\pmb{\theta})$ 
%ZH: we should add 2 sentences on how you measured kappa.  Directly from the ray-tracing?
%   (but above, when you discuss ray-tracing, you mention only gamma).  Or did you do 
%    Kaiser-Squires on the gamma field ? 
and measure its
angular power spectrum $P^{\kappa\kappa}_r(l)$ defined as
\begin{equation}
\langle\tilde{\kappa}_r(\bb{l})\tilde{\kappa}_r(\bb{l}')\rangle = (2\pi)^2\delta_D(\bb{l}+\bb{l}')P^{\kappa\kappa}_r(l)
\end{equation}
%
As an additional summary statistic, we consider the counts of local
$\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$
(hereafter \textit{peak counts}), with varying $\kappa_0$.
%ZH: state here the range and binning choice of $\kappa_0$
The fact that the ensemble of $N_r$ realizations is not completely
independent if $N_s$ is not large enough can have an effect on the
covariance estimators of both $P^{\kappa\kappa}$ and $n(\kappa_0)$.

%ZH: it would be logical to mention the other w,Sig,Om, sims here, and point to \ref{simtable})

@@

To measure the derivatives of the features $\bb{d}'_0$ with respect to
the cosmological parameters, we make use of the public code
\texttt{NICAEA} \citep{Nicaea} for the power spectrum, and we use an
independent simulation set (containing simulations with a variety of
different combinations of $(\Omega_m,w,\sigma_8)$, see Table
\ref{simtable}) for the peak counts.

\begin{table}
\begin{center}
\begin{tabular}{c|c|c||c|c}
\toprule
$\Omega_m$ &  $w$ & $\sigma_8$ & $N_s$ & Number of $\kappa$ ensembles \\ \hline \hline
\midrule
%
0.26 & -1 & 0.8 & $1$ to $200$ & 16 \\
0.29 & -1 & 0.8 & 1 & 1 \\
0.26 & -0.8 & 0.8 & 1 & 1 \\
0.26 & -1 & 0.6 & 1 & 1 \\
%
\bottomrule
\end{tabular}
\end{center}
\caption{Summary of the shear ensembles used in this work.}
%ZH: So each of these have N_r=1000, yes?  You should state this here. And also,
%    Add the ensemble with N_s=1, N_r=10^5 to this table.
%    Also: point the reader to this table in the text, up front, when the 
%    ensembles are first discussed.
\label{simtable}
\end{table}

@@

\begin{figure}
\includegraphics[scale=0.3]{Figures/means_ns.eps}
\caption{The mean value 
 $\bb{\bar{d}}$
% $d$  
%ZH: I think you mean  \bb{\bar{d}} here?  You introduced a lot of different
%    subtle notations in the previous section, so we should  follow those ....
  of various features, measured from ensembles created from different
  numbers $N_s$ of simulations.  For each case, the difference compared
  to the mean in the $N_s=200$ ensemble is shown, in units of the
  statistical error measured in the $N_s=200$ ensemble.  The colored
  curves refer to shear-shear power spectra measured at $\ell=115$
  (black), 1027 (cyan), and 5283 (green), and peak counts 
%of
%ZH: I replace ``of'' with ``above''.  These are cumulative peak counts N(>kappa_0) ?
%    Or do you mean differential counts in some delta-kappa_0 bins?   Then you should
%    correct the text (and state the bin width).  Table II contains some kappa-bins
%    but no obvious relation to the 0.05, 0.17  and 0.28 mentioned here...
  with height above $\kappa_0=0.05$ (red), 0.17 (purple), and 0.28
  (orange).  For $N_s\geq 2$, the means are statistically
  indistinguishable from the means measured in the ensemble with $N_s=200$.}
% added last sentence stating conclusion to be drawn from the figure-Morgan
%ZH:  Good idea.  All figures captions should similarly state a conclusion!
%ZH:  What is the horizontal dashed line?  It is never mentioned in the caption or
%     the text.   I guess you decided to mark the ``0.1 sigma'' deviation?
%     We should state that.    I suppose this is what Morgan refers to by 
%    ``statistically indistinguishable'' ....  0.1 sigma.
\label{means_ns}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.3]{Figures/curving_nb.eps}
\caption{Expectation value of the variance of $w$ computed from
  equation (\ref{estimatorcovariance}), shown as a function of
  $1/N_r$. The different symbols and colors correspond to the features
  listed in Table~\ref{featuretable}.
%ZH: It would be better to write the features on the legend embedded in the figure.
%    Why make the reader flip back-and-forth between the figure and the Table ?
  The dashed and solid curves show the analytic predictions from
  equation (\ref{quarticdegradation}) at orders $O(1/N_r)$ and
  $O(1/N_r^2)$, respectively. The asymptotic variance
  $\sigma^2_{w,\infty}$ has been computed from a linear regression of
  $\langle\h{\sigma}^2_w\rangle$ vs $1/N_r$ for $N_r>500$. The figure
  clearly shows that terms beyond $O(1/N_r)$ need to be considered,
  unless $N_r\gg N_b$.}
%added last sentence stating conclusion to be drawn from the figure-Morgan
%in legend box change line that reads Nb=7 divided by 8
\label{curvingnb}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.3]{Figures/scaling_ns.eps}
\caption{The variance of $w$ in the limit of $N_r\rightarrow\infty$,
%ZH: state here what N_r was actually used to approximate the infinity limit
  varying the number of simulations $N_s$ used in the ensemble to
  estimate the covariance (eq.~\ref{covest}). We show the dependence
  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over $N_s$, 
%ZH: Just to make sure: what you mean here is an averaging of sigma_infty over the 16 different
%    cases of N_s ?   
  for
  the power spectrum logarithmically binned (black), the power
  spectrum linearly binned (red) and the peak counts (green).
%ZH: What ell and kappa ranges were used?
%XH: Added conclusion:
  No trend with $N_s$ is seen for $N_s\geq 2$, and the
  differences are only 1\%.  }
\label{wvar_ns}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%% APPENDIX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%ZH: I did not carefully re-read the appendices.  I guess that is OK.
%    One cosmetic comment:  when you refer to equations, you need to say
%    ``as in eq. (xx)''  rather than  ``as in (xx)''.
%    
\section*{Appendix A: cubic and quartic covariance fluctuations}
\label{appendixA}

The goal of this appendix is to give a derivation of equation (\ref{quarticdegradation}). When the simulated feature vector $\bbh{d}_r$ is drawn from a Gaussian distribution, the covariance estimator $\bbh{C}$ follows the Wishart distribution, and its inverse $\bbh{\Psi}$ follows the inverse Wishart distribution. For the analytical expressions of these probability distributions we remand the reader to \citep{Taylor12}. Computing expectation values of (\ref{estimatorcovariance}) over the inverse Wishart distribution is not possible analytically, and a perturbative expansion is necessary. Writing $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$, we can expand equation (\ref{quarticdegradation}) in powers of $\delta\bbh{\Psi}$. The expectation values of each term in this perturbative expansion can be calculated in term of the moments of the inverse Wishart distribution. \citep{MasumotoWishart} provide a general framework to compute these moments, and give exact expressions for moments up to quartic order. First, let us expand the inverse of the Fisher matrix estimator (\ref{estimatorfisher}) in powers of $\delta\bbh{\Psi}$. The $n$--th order of this expansion will be

\begin{equation}
\label{nthterm}
\delta\bbh{F}^{-1}_{(n)} = (-1)^{n}(\bb{F}^{-1}\delta\bbh{F})^n\bb{F}^{-1}
\end{equation}
%
with
\begin{equation}
\delta\bbh{F} = \bb{d}_0'^T\delta\bbh{\Psi}\bb{d}_0'
\end{equation}
%
Using (\ref{nthterm}), we can expand (\ref{estimatorcovariance}) to an arbitrary order in $\delta\bbh{\Psi}$, take the expectation values of the fluctuations over the inverse Wishart distribution, and finally get to (\ref{quarticdegradation}). We use the notation $\nu=N_r-1$ and $\gamma=(\nu-N_b-1)/2$. We indicate with capital letters pairs of matrix indices, for example $I=(i_1,i_2)$, where $i_a=1..N_b$. The main results we take out from \citep{MasumotoWishart} regarding the first four moments are (up to order $O(1/\nu^2)$)

@@

\end{cases}
\end{equation}
\end{widetext}
%
When the results from (\ref{expansionbreakdown}) are summed, (\ref{quarticdegradation}) immediately follows.

>>>>

%ZH: I changed to more catchy title:
%\title{Simulating sample variance in weak lensing: effects on parameter inferences}
%AP: Ok

\title{Sample variance in weak lensing: how many simulations are required?}

@@

Constraining cosmology using weak gravitational lensing consists of
comparing a measured feature vector of dimension $N_b$ with its
simulated counterpart. An accurate estimate of the $N_b\times N_b$
feature covariance matrix $\bb{C}$ is essential to obtain accurate
parameter confidence intervals. When $\bb{C}$ is measured from a set
of simulations, an important question is how large this set should
be. To answer this question, we construct different ensembles of $N_r$
realizations of the shear field, using a common randomization
procedure that recycles the outputs from a smaller number $N_s\leq
N_r$ of independent ray-tracing $N$--body simulations.  We study
parameter confidence intervals as a function of ($N_s,N_r$) in the
range $1\leq N_s\leq 200$ and $1\leq N_r\leq 10^5$.  Previous work
\citep{DodelsonSchneider13} has shown that Gaussian noise in the
feature covariance lead, at quadratic order, to an $O(1/N_r)$
degradation of the parameter confidence intervals. Using a variety of
lensing features measured in our simulations, including shear-shear
power spectra and peak counts, we show that cubic and quartic
covariance fluctuations lead to additional $O(1/N_r^2)$ error
degradation that is not negligible when $N_r$ is only a factor of few
larger than $N_b$. We study the large $N_r$ limit, and find that a
single $N$--body simulation ($N_s=1$) can be repeatedly recycled to
produce as many as $N_r=10^5$ mutually independent shear maps. As a
result, a small number of simulations ($N_s=1$ or $2$) is sufficient
to forecast parameter confidence intervals at percent
accuracy.

%However, we find that in practice, a larger number of
%simulations might be needed to measure accurate feature means and to
%avoid parameter biases.
%ZH: I am not sure about the last sentence. I believe it is based on
%    an overly stringent reading of Fig.2, and that in fact we could
%    claim here, instead, that N_s=2 simulations are also sufficient
%    to get the correct mean.
%    See my comments at the end of the Conclusion section.

%AP: Ok, sentence removed

\end{abstract}

@@

\section{Introduction}
%
Weak gravitational lensing (WL) is a promising cosmological probe for
constraining the dark energy equation of state $w$, and has been
considered by a range of past (CFHTLens \citep{cfht1,cfht2}, COSMOS \citep{cosmos}),
%ZH: also cite COSMOS survey here...
%AP: done
ongoing (DES \citep{DES}) and future (LSST \citep{LSST}, Euclid \citep{Euclid}, WFIRST \citep{WFIRST})
%ZH: also cite Euclid and WFIRST.
%AP: done
experiments. In an era where cosmology is data driven, accurate
numerical simulations of shear fields are becoming important for
several reasons, including the study of baryonic effects
\citep{BaryonXiuyuan,BaryonSemboloni,BaryonsWhite,BaryonsKnox,BaryonsZentner1,BaryonsZentner2}, 
%ZH: also cite Joop Schaye's hydro-simulation papers on lensing (Semboloni et al), and earlier papers by Martin White et al...  Lloyd Knox et al... and Zentner et al... (I think all of these are in Xiuyuan's paper).
%AP: done
the computation of non--Gaussian statistics
\citep{PeaksJan,MinkJan,MinkPetri,NG-Marian,NG-Jain1,NG-Jain2,NG-Jain3,NG-Refregier,NG-Dietrich} 
%ZH: Add here some citations of other groups - Marian+Bernstein.... Bhuvnesh Jain et al... Refregier et al... Dietrichh+Hartmann... Shirasaki+Yoshida.. (again just copy from our previous papers).
%AP: done
and the  assessment of various systematics
\citep{MinkShirasaki,Sys-Bard,Sys-Chang,Sys-Huterer}.
%ZH: cite papers by Jan+Morgan+Bard... and also Chihway Chan...Shirasaki+Yoshida.. and older ones by Dragan Huterer on photo-z errors..
%AP: done

A fundamental issue with predictions from simulations is that the
finite number of simulations naturally introduces fluctuations in the
forecasts, due to inevitable sample variance~\footnote{Sample variance is a broad term that has been used in the literature to describe a range of phenomena.  Throughout this paper, we use it to refer to the fluctuations in an ensemble of simulations, which represent random realizations of the same initial conditions.}.
%ZH: I think 'cosmic variance' usually refers to observations of the actual sky (which is finite). 
%AP: OK 
In general, quantities such as the mean or the variance of any feature
(e.g. the shear power spectrum at a multipole $\ell$), measured from a
finite set of simulations, will fluctuate, and can also suffer a bias.
While biases in the estimates of both the mean and the variance have
been studied extensively, the impact of fluctuations in the variance
has received comparatively less attention.  These fluctuations have,
however, been shown to have non-negligible effects on estimates of
features covariance matrices and hence on parameter constraints. In
particular, in the limit of Gaussian fluctuations, the parameter
confidence limits are degraged by a factor
$1+O(1/N_r)$~\citep{DodelsonSchneider13,Taylor12}.
%MM: also cite Taylor Joachimi and Kitching
%AP: done

@@

\subsection{Ray-tracing simulations of the convergence field}
\label{shearsim}
%
In this section, we describe how we constructed our shear field
ensembles. Background galaxies at redshift $z_s$ are lensed by large
scale structures between $z=0$ and $z_s$. The shape distortions due to
the cosmic shear $\pmb{\gamma}$ can be computed in terms of the dark
matter gravitational potential $\Phi(\bb{x},z)$. Because the evolution
of $\Phi$ with redshift is non--linear, it needs to be computed with
numerical simulations. We make use of the public code \texttt{Gadget2}
\citep{Gadget2}, with which we run a sequence of $200$ independent
dark--matter--only $N$--body simulations that track the evolution of
the density fluctuations. We assume a standard $\Lambda$CDM background
universe with the parameters
$(\Omega_m,\Omega_\Lambda,h,w,\sigma_8,n_s)=(0.26,0.74,0.72,-1,0.8,0.96)$.
We fix the comoving size of the simulation box to $240\mathrm{Mpc}/h$,
and use $512^3$ particles, corresponding to a Dark Matter particle mass of
$\approx 10^{10}M_\odot$.
%ZH: ``mass resolution'' here means DM particle mass ?
%AP: fixed

We assume a uniform galaxy distribution at a constant redshift $z_s=2$
(at which the simulation box has an angular size of $\theta_{\rm
  box}=3.5\mathrm{deg}$) and we discretize the mass distribution
between $z_s$ and the observer at $z=0$ with a sequence of 46 two
dimensional lenses of thickness $80\mathrm{Mpc}/h$. The surface
density on each lens plane is computed by projecting the
three--dimensional density measured from \texttt{Gadget2}
snapshots. We then apply the multi--lens--plane algorithm (see
\citep{RayTracingHartlap,RayTracingJain} for example) to trace the
deflections of $n_{\rm ray}^2=2048^2$ light rays arranged on a square grid
of total size $\theta_{\rm box}$, from $z=0$ to $z_s$. Our
implementation of this algorithm is part of the \texttt{LensTools}
computing package we have been developing \citep{LensTools}, and have
released under the \texttt{MIT} license. Many different realizations
$r$ of the same shear field $\pmb{\gamma}_r(\pmb{\theta})$ can be
generated by picking different lens planes that lie between the
observer and $z_s$. The randomization procedure we adopt is the
following (see \citep{Sato12} for reference):
%ZH: we should cite some paper here. We didn't invent most of this
%procedure ourselves (except for maybe the 3-times thicker simulation
%output, and the random mixing of the planes from different N-body sims ?).
%AP: I added the citation to Sato et. al, which refer to this procedure without citing anyone

\begin{itemize}
\item For each lens-plane redshift $z_l$, select the snapshot at $z_l$ from the $i$--th $N$--body simulation, where $i$ is a random integer $i\in [1,N_s]$.
\item Choose randomly between the three orthogonal directions ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$: the lens plane will be perpendicular to this direction.
\item Choose the position of the plane along the snapshot: because the lens thickness is 1/3 the size of the box, we can cut three different slices of the simulation box for each orientation ${\bb{n}_x,\bb{n}_y,\bb{n}_z}$. This gives a total of 9 choices for generating a lens plane out of a single $N$--body snapshot.
\item Perform a periodic random shift of the lens plane along its two directions.
%ZH: should we specify the range of the random shifts (0 to 1/2 the lens plane dimension?)
%AP: This is not necessary, since the shifts are periodic, in principle one could choose a random number of pixels. In particular this number should be between 0 and 4095, because each lens plane has 4096 pixels
\item Repeat the above procedure for each lens-plane redshift $z_l$.
\end{itemize}  
%
This randomization procedure allows us to produce an (almost)
arbitrary number $N_r$ of shear realizations
$\pmb{\gamma}_r(\pmb{\theta})$. However, these realizations are not
guaranteed to be independent, if $N_s$ is not large enough. Using the
set of 200 independent $N$--body simulations, we construct different
ensembles with different choices of $N_s\in[1,200]$. Each of these
ensembles consists of the same number $N_r=1000$ of shear
realizations. We also build an additional ensemble with $N_s=1$ and
$N_r=10^5$ realizations. For each realization of each ensemble, we
reconstruct the convergence $\kappa_r(\pmb{\theta})$ from the trace of the light ray deflection Jacobian matrix, measured looking at the difference in angle deflection between nearby light rays \citep{RayTracingHartlap,RayTracingJain,Sato12}.
%ZH: we should add 2 sentences on how you measured kappa.  Directly from the ray-tracing?
%   (but above, when you discuss ray-tracing, you mention only gamma).  Or did you do 
%    Kaiser-Squires on the gamma field ? 
%AP: done, we measure kappa directly from the ray tracing

We measure the $\kappa$ angular power spectrum $P^{\kappa\kappa}_r(\ell)$ defined as
\begin{equation}
\langle\tilde{\kappa}_r(\pmb{\ell})\tilde{\kappa}_r(\pmb{\ell}')\rangle = (2\pi)^2\delta_D(\pmb{\ell}+\pmb{\ell}')P^{\kappa\kappa}_r(\ell)
\end{equation}
%
As an additional summary statistic, we consider the counts of local
$\kappa$ maxima of a certain height $\kappa_0$, $n_r(\kappa_0)$
(hereafter \textit{peak counts}), with varying $\kappa_0$.
%ZH: state here the range and binning choice of $\kappa_0$
The fact that the ensemble of $N_r$ realizations is not completely
independent if $N_s$ is not large enough can have an effect on the
covariance estimators of both $P^{\kappa\kappa}$ and $n(\kappa_0)$.

%ZH: it would be logical to mention the other w,Sig,Om, sims here, and point to \ref{simtable})
%AP: done, added the below

To measure the cosmological dependence of the $\kappa$ peak counts, we also performed additional ray--tracing simulations with different combinations of the cosmological parameter triplet $(\Omega_m,w,\sigma_8)$ as outlined in Table \ref{simtable}.

@@

To measure the derivatives of the features $\bb{d}'_0$ with respect to
the cosmological parameters, we make use of the public code
\texttt{Nicaea} \citep{Nicaea} for the power spectrum, and we use an
independent simulation set (containing simulations with a variety of
different combinations of $(\Omega_m,w,\sigma_8)$, see Table
\ref{simtable}) for the peak counts.

\begin{table}
\begin{center}
\begin{tabular}{c|c|c||c|c|c}
\toprule
$\Omega_m$ &  $w$ & $\sigma_8$ & $N_s$ & $N_r$ & Number of $\kappa$ ensembles \\ \hline \hline
\midrule
%
0.26 & $-$1 & 0.8 & $1\div200$ & $1024\div128000$ & 16 \\
0.29 & $-$1 & 0.8 & 1 & 1024 & 1 \\
0.26 & $-$0.8 & 0.8 & 1 & 1024 & 1 \\
0.26 & $-$1 & 0.6 & 1 & 1024 & 1 \\
%
\bottomrule
\end{tabular}
\end{center}
\caption{Summary of the shear ensembles used in this work.}
%ZH: So each of these have N_r=1000, yes?  You should state this here. And also,
%    Add the ensemble with N_s=1, N_r=10^5 to this table.
%    Also: point the reader to this table in the text, up front, when the 
%    ensembles are first discussed.
\label{simtable}
\end{table}

@@

\begin{figure}
\includegraphics[scale=0.3]{Figures/means_ns.eps}
\caption{The mean value 
 $\bb{\bar{d}}$
% $d$  
%ZH: I think you mean  \bb{\bar{d}} here?  You introduced a lot of different
%    subtle notations in the previous section, so we should  follow those ....
  of various features, measured from ensembles created from different
  numbers $N_s$ of simulations.  For each case, the difference compared
  to the mean in the $N_s=200$ ensemble is shown, in units of the
  statistical error measured in the $N_s=200$ ensemble.  The colored
  curves refer to shear-shear power spectra measured at $\ell=115$
  (black), 1027 (cyan), and 5283 (green), and peak counts 
%of
%ZH: I replace ``of'' with ``above''.  These are cumulative peak counts N(>kappa_0) ?
%    Or do you mean differential counts in some delta-kappa_0 bins?   Then you should
%    correct the text (and state the bin width).  Table II contains some kappa-bins
%    but no obvious relation to the 0.05, 0.17  and 0.28 mentioned here...
  with height above $\kappa_0=0.05$ (red), 0.17 (purple), and 0.28
  (orange).  For $N_s\geq 2$, the means are statistically
  indistinguishable from the means measured in the ensemble with $N_s=200$.}
%MM: added last sentence stating conclusion to be drawn from the figure
%ZH:  Good idea.  All figures captions should similarly state a conclusion!
%ZH:  What is the horizontal dashed line?  It is never mentioned in the caption or
%     the text.   I guess you decided to mark the ``0.1 sigma'' deviation?
%     We should state that.    I suppose this is what Morgan refers to by 
%    ``statistically indistinguishable'' ....  0.1 sigma.
\label{means_ns}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.3]{Figures/curving_nb.eps}
\caption{Expectation value of the variance of $w$ computed from
  equation (\ref{estimatorcovariance}), shown as a function of
  $1/N_r$. The different symbols and colors correspond to the features
  listed in Table~\ref{featuretable}.
%ZH: It would be better to write the features on the legend embedded in the figure.
%    Why make the reader flip back-and-forth between the figure and the Table ?
  The dashed and solid curves show the analytic predictions from
  equation (\ref{quarticdegradation}) at orders $O(1/N_r)$ and
  $O(1/N_r^2)$, respectively. The asymptotic variance
  $\sigma^2_{w,\infty}$ has been computed from a linear regression of
  $\langle\h{\sigma}^2_w\rangle$ vs $1/N_r$ for $N_r>500$. The figure
  clearly shows that terms beyond $O(1/N_r)$ need to be considered,
  unless $N_r\gg N_b$.}
%MM: added last sentence stating conclusion to be drawn from the figure
%in legend box change line that reads Nb=7 divided by 8
\label{curvingnb}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.3]{Figures/scaling_ns.eps}
\caption{The variance of $w$ in the limit of $N_r\rightarrow\infty$,
%ZH: state here what N_r was actually used to approximate the infinity limit
  varying the number of simulations $N_s$ used in the ensemble to
  estimate the covariance (eq.~\ref{covest}). We show the dependence
  of $\sigma_{w,\infty}^2(N_s)$ in units of the mean over $N_s$, 
%ZH: Just to make sure: what you mean here is an averaging of sigma_infty over the 16 different
%    cases of N_s ?   
  for
  the power spectrum logarithmically binned (black), the power
  spectrum linearly binned (red) and the peak counts (green).
%ZH: What ell and kappa ranges were used?
%ZH: Added conclusion:
  No trend with $N_s$ is seen for $N_s\geq 2$, and the
  differences are only 1\%.  }
\label{wvar_ns}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%% APPENDIX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%ZH: I did not carefully re-read the appendices.  I guess that is OK.
%    One cosmetic comment:  when you refer to equations, you need to say
%    ``as in eq. (xx)''  rather than  ``as in (xx)''.
%AP: done   
\section*{Appendix A: cubic and quartic covariance fluctuations}
\label{appendixA}

The goal of this appendix is to give a derivation of eq. (\ref{quarticdegradation}). When the simulated feature vector $\bbh{d}_r$ is drawn from a Gaussian distribution, the covariance estimator $\bbh{C}$ follows the Wishart distribution, and its inverse $\bbh{\Psi}$ follows the inverse Wishart distribution. For the analytical expressions of these probability distributions we remand the reader to \citep{Taylor12}. Computing expectation values of eq. (\ref{estimatorcovariance}) over the inverse Wishart distribution is not possible analytically, and a perturbative expansion is necessary. Writing $\bbh{\Psi}=\bb{\Psi}+\delta\bbh{\Psi}$, we can expand eq. (\ref{quarticdegradation}) in powers of $\delta\bbh{\Psi}$. The expectation values of each term in this perturbative expansion can be calculated in term of the moments of the inverse Wishart distribution. \citep{MasumotoWishart} provide a general framework to compute these moments, and give exact expressions for moments up to quartic order. First, let us expand the inverse of the Fisher matrix estimator (\ref{estimatorfisher}) in powers of $\delta\bbh{\Psi}$. The $n$--th order of this expansion will be

\begin{equation}
\label{nthterm}
\delta\bbh{F}^{-1}_{(n)} = (-1)^{n}(\bb{F}^{-1}\delta\bbh{F})^n\bb{F}^{-1}
\end{equation}
%
with
\begin{equation}
\delta\bbh{F} = \bb{d}_0'^T\delta\bbh{\Psi}\bb{d}_0'
\end{equation}
%
Using eq. (\ref{nthterm}), we can expand eq. (\ref{estimatorcovariance}) to an arbitrary order in $\delta\bbh{\Psi}$, take the expectation values of the fluctuations over the inverse Wishart distribution, and finally get to eq. (\ref{quarticdegradation}). We use the notation $\nu=N_r-1$ and $\gamma=(\nu-N_b-1)/2$. We indicate with capital letters pairs of matrix indices, for example $I=(i_1,i_2)$, where $i_a=1..N_b$. The main results we take out from \citep{MasumotoWishart} regarding the first four moments are (up to order $O(1/\nu^2)$)

@@

\end{cases}
\end{equation}
\end{widetext}
%
When the results from eq. (\ref{expansionbreakdown}) are summed, eq. (\ref{quarticdegradation}) immediately follows.
